Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-08-17 article.tex
Added city for RIT
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1364 ccdd05d5-56c1-461a-bf98-85f6876523b4

\altaffiltext{1}{Canadian Institute for Theoretical Astrophysics, Toronto, ON, Canada}
\altaffiltext{2}{D\'{e}partement de physique, \'{E}cole Normale Sup\'{e}rieure de Cachan, Cachan, France}
\altaffiltext{3}{LIGO Laboratory, California Institute of Technology, MC 100-36, 1200 E. California Blvd., Pasadena, CA, USA; \texttt{leo.singer@ligo.org}}
\altaffiltext{4}{Facultat de F\'{i}sica, Universitat de Val\`{e}ncia, Burjassot, Spain} 
\altaffiltext{5}{University of Texas at Austin, Austin, TX, USA}
\altaffiltext{6}{Center for Computational Relativity and Gravitation and School of Mathematical Sciences, Rochester Institute of Technology, NY, USA}
\altaffiltext{7}{Perimeter Institute for Theoretical Physics, Waterloo, ON, Canada}
\altaffiltext{8}{Department of Physics and Astronomy, Barnard College, Columbia University, New York, NY, USA}
\altaffiltext{9}{Albert-Einstein-Institut, Max-Planck-Institut f\"{u}r Gravitationphysik, Hannover, Germany}
\altaffiltext{10}{Leibniz Universit\"{a}t Hannover, Hannover, Germany}
\altaffiltext{11}{Ryerson University, Toronto, ON, Canada}

>>>>

\altaffiltext{1}{Canadian Institute for Theoretical Astrophysics, Toronto, ON, Canada}
\altaffiltext{2}{D\'{e}partement de physique, \'{E}cole Normale Sup\'{e}rieure de Cachan, Cachan, France}
\altaffiltext{3}{LIGO Laboratory, California Institute of Technology, MC 100-36, 1200 E. California Blvd., Pasadena, CA, USA; \texttt{leo.singer@ligo.org}}
\altaffiltext{4}{Facultat de F\'{i}sica, Universitat de Val\`{e}ncia, Burjassot, Spain} 
\altaffiltext{5}{University of Texas at Austin, Austin, TX, USA}
\altaffiltext{6}{Center for Computational Relativity and Gravitation and School of Mathematical Sciences, Rochester Institute of Technology, Rochester, NY, USA}
\altaffiltext{7}{Perimeter Institute for Theoretical Physics, Waterloo, ON, Canada}
\altaffiltext{8}{Department of Physics and Astronomy, Barnard College, Columbia University, New York, NY, USA}
\altaffiltext{9}{Albert-Einstein-Institut, Max-Planck-Institut f\"{u}r Gravitationphysik, Hannover, Germany}
\altaffiltext{10}{Leibniz Universit\"{a}t Hannover, Hannover, Germany}
\altaffiltext{11}{Ryerson University, Toronto, ON, Canada}
